\Huge ACM and Climate Change

### 2018-12-26 main.tex
todo

Why ACM? Because one of ACM's main activities is organizing international
conferences, which produce significant emissions of greenhouse gases,
particularly from air travel. For example, a single round-trip flight from
Philadelphia to Paris emits the equivalent of about 1.7 tons of carbon
dioxide (\COtwoE) per passenger~\cite{carboncalculator}\iflater\bcp{Trim
  citation?}\fi---a substantial fraction of the {\em total} yearly emissions
for an average resident of the US (16.5 tons) or Europe (7
tons)~\cite{emissions}.  Moreover, these emissions have no near-term
technological fix because jet fuel is difficult to replace with
renewable energy sources~\cite{elec-air}. 
\iflater\bcp{Trimmed this sentence: Reducing the \COtwoE{} footprint
of conferences will require a reduction in the footprint of the attendees'
air travel.}\fi

>>>>

Why ACM? Because one of ACM's main activities is organizing international
conferences, which produce significant emissions of greenhouse gases,
particularly from air travel. For example, a single round-trip flight from
Philadelphia to Paris emits the equivalent of about 1.7 tons of carbon
dioxide (\COtwoE) per passenger~\cite{carboncalculator}\iflater\bcp{Trim
  citation?}\fi---a substantial fraction of the {\em total} yearly emissions
for an average resident of the US (16.5 tons) or Europe (7
tons)~\cite{emissions}.  \iflater\bcp{For comparison, ...  (put in some
  figures about the footprints of a few other things that people might think
  of reducing---driving, eating meat, upgrading their fridge...)}\fi{}
Moreover, these emissions have no near-term 
technological fix because jet fuel is difficult to replace with
renewable energy sources~\cite{elec-air}. 
\iflater\bcp{Trimmed this sentence: Reducing the \COtwoE{} footprint
of conferences will require a reduction in the footprint of the attendees'
air travel.}\fi
